---
title: "Rodrigo Aroni Siquette CV"
author: rodrigo
date: "`r Sys.Date()`"
output:
  pagedown::html_resume:
    css: ['css/styles.css', 'resume']
    # set it to true for a self-contained HTML page but it'll take longer to render
    self_contained: true
---




```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)

library(glue)
library(tidyverse)
library(pagedown)

# Set this to true to have links turned into footnotes at the end of the document
PDF_EXPORT <- FALSE

# Holds all the links that are inserted for placement at the end
links <- c()

source('parsing_functions.R') # Functions for building sections from CSV data
source('common_variables.R')  # Small variables for non-csv data such as intro text

# Load csv with position info
position_data <- read_csv('positions.csv')
```


```{r}
# When in export mode the little dots are unaligned, so fix that. 
if(PDF_EXPORT){
  cat("
  <style>
  :root{
    --decorator-outer-offset-left: -6.5px;
  }
  </style>")
}
```

::: aside

<div id="interactive-globe" style="width: 160px; height: 160px; margin: -25px auto 5px auto; border-radius: 50%; overflow: hidden; border: 2px solid #bdd7e7;"></div>

<script src="https://d3js.org/d3.v7.min.js"></script>
<script src="https://unpkg.com/topojson-client@3"></script>
<script>
window.addEventListener("load", function() {
    const width = 160; const height = 160; 
    const sensitivity = 75; const rotationSpeed = 0.3;
    const containerId = "#interactive-globe";
    
    d3.select(containerId).selectAll("*").remove();
    const svg = d3.select(containerId).append("svg")
      .attr("width", width).attr("height", height)
      .style("display", "block").style("margin", "auto");

    const projection = d3.geoOrthographic()
      .scale(79).center([0, 0]).rotate([0, -30])
      .translate([width / 2, height / 2]);

    let path = d3.geoPath().projection(projection).pointRadius(1.5);
    const CONNECTION_COLOR = "#08306b"; 

    svg.append("circle").attr("cx", width/2).attr("cy", height/2)
      .attr("r", projection.scale()).attr("fill", "#ADD8E6").attr("stroke", "none");

    const mapGroup = svg.append("g"); const linesGroup = svg.append("g"); const particlesGroup = svg.append("g");
    let isAutoRotating = true; let isDragging = false; let activeLinks = []; 

    function redraw() {
        path = d3.geoPath().projection(projection).pointRadius(1.5);
        svg.selectAll("path.country").attr("d", path);
        svg.selectAll("path.connection").attr("d", path);
        svg.selectAll("path.particle").attr("d", function(d) { return d.currentCoords ? path({type: "Point", coordinates: d.currentCoords}) : null; });
    }

    d3.json("https://cdn.jsdelivr.net/npm/world-atlas@2/countries-110m.json").then(function(world) {
        const countries = topojson.feature(world, world.objects.countries).features;
        const globePaths = mapGroup.selectAll("path.country").data(countries).enter().append("path")
          .attr("class", "country").attr("d", path).attr("fill", "#FFFFFF") 
          .attr("stroke", "#444").attr("stroke-width", "0.3px").style("cursor", "grab");

        const drag = d3.drag()
            .on("start", function() { isDragging = true; isAutoRotating = false; d3.select(this).style("cursor", "grabbing"); })
            .on("drag", function(event) {
                const rotate = projection.rotate();
                const k = sensitivity / projection.scale();
                projection.rotate([rotate[0] + event.dx * k, rotate[1] - event.dy * k]);
                redraw(); 
            })
            .on("end", function() { isDragging = false; isAutoRotating = true; d3.select(this).style("cursor", "grab"); });
        svg.call(drag);

        globePaths.on("mouseover", function() { if (!isDragging) { isAutoRotating = false; d3.select(this).attr("fill", "#bdd7e7"); } })
                  .on("mouseout", function() { if (!isDragging) { isAutoRotating = true; d3.select(this).attr("fill", "#FFFFFF"); } });

        d3.interval(function() {
            const numNewLinks = 10; 
            if (activeLinks.length > 24) activeLinks = activeLinks.slice(4);
            for (let i = 0; i < numNewLinks; i++) {
                const source = countries[Math.floor(Math.random() * countries.length)];
                const target = countries[Math.floor(Math.random() * countries.length)];
                if (source && target) {
                    const s = d3.geoCentroid(source); const t = d3.geoCentroid(target);
                    const linkData = { type: "LineString", coordinates: [s, t], source: s, target: t, id: Date.now()+Math.random(), currentCoords: s };
                    activeLinks.push(linkData); createLinkAndParticle(linkData);
                }
            }
        }, 1200);

        function createLinkAndParticle(linkData) {
            linesGroup.append("path").datum(linkData).attr("class", "connection").attr("d", path)
                .attr("fill", "none").attr("stroke", CONNECTION_COLOR).attr("stroke-width", "2px") 
                .attr("stroke-dasharray", "2,2").style("opacity", 0.5).style("pointer-events", "none")
                .transition().duration(3000).style("opacity", 0).remove();

            const particle = particlesGroup.append("path").datum(linkData).attr("class", "particle")
                .attr("fill", CONNECTION_COLOR).attr("d", path({type: "Point", coordinates: linkData.source}))
                .style("pointer-events", "none");
            
            const interpolator = d3.geoInterpolate(linkData.source, linkData.target);
            particle.transition().duration(2000 + Math.random() * 1000).ease(d3.easeQuadInOut)
                .tween("route", function(d) { return function(t) { d.currentCoords = interpolator(t); d3.select(this).attr("d", path({type: "Point", coordinates: d.currentCoords})); }; })
                .remove();
        }

        d3.timer(function() {
            if (!isDragging && isAutoRotating) {
                const rotate = projection.rotate(); projection.rotate([rotate[0] + rotationSpeed, rotate[1]]); redraw();
            }
        });
    }).catch(err => console.error(err));
});
</script>

<h2 style="margin-top: 5px !important;"><i class="fa fa-github"></i> [Portfólio](https://siquette.github.io/portifolio_3/)</h2>

<h2>Contato</h2>
<ul>
<li><i class="fa fa-envelope"></i> rodrigo.siquette@usp.br</li>
<li><i class="fa fa-envelope"></i> rodrigoaronisiquette@gmail.com</li>
<li><i class="fa fa-linkedin-square"></i> [linkedin.com/in/rodrigo-aroni-siquette](https://www.linkedin.com/in/rodrigo-aroni-siquette/)</li>
<li><i class="fa fa-phone"></i> (19) 995504223</li>
</ul>

<h2>Competências Técnicas</h2>

<div class="skill-group">
<strong>Linguagens & Análise</strong>
<i class="fab fa-python fa-fw"></i> Python <span>(Pandas, Scikit-Learn, TensorFlow)</span><br>
<i class="fab fa-r-project fa-fw"></i> R <span>(Tidyverse, Shiny)</span><br>
<i class="fas fa-database fa-fw"></i> SQL
</div>

<div class="skill-group">
<strong>Geoespacial</strong>
<i class="fas fa-map-marked-alt fa-fw"></i> ArcGIS <br>
<i class="fas fa-globe-americas fa-fw"></i> QGIS<br>
<i class="fas fa-layer-group fa-fw"></i> GeoPandas<br>
<i class="fas fa-database fa-fw"></i> PostGIS
</div>

<div class="skill-group">
<strong>Ferramentas & DevOps</strong>
<i class="fab fa-git-alt fa-fw"></i> Git / GitHub<br>
<!-- <i class="fab fa-docker fa-fw"></i> Docker<br> -->
<i class="fab fa-markdown fa-fw"></i> Markdown / LaTeX
</div>

:::



Main
================================================================================

Rodrigo Aroni Siquette {#title}
--------------------------------------------------------------------------------



<p align="justify"> Cientista de Dados e Geógrafo (USP) com sólida formação acadêmica e foco em Inteligência Espacial. Especialista na transformação de dados complexos em soluções estratégicas através de modelagem estatística, Python e SQL. Experiência comprovada em análise de alocação territorial e inteligência de mercado, unindo rigor científico com agilidade de negócios. </p>

<p align="justify">Vamos bater um papo? </p>
 



Formação  {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

```{r}
print_section(position_data, 'education')
```

Experiência Profissional {data-icon=suitcase}
--------------------------------------------------------------------------------
```{r}
print_section(position_data, 'industry_positions')
```

Atividades extra curriculares {data-icon=laptop}
--------------------------------------------------------------------------------

```{r}
print_section(position_data, 'research_positions')
```



::: aside
 
:::



<br>
<br>
<br>





```{r}
if(PDF_EXPORT){
  cat("
  
Links {data-icon=link}
--------------------------------------------------------------------------------

<br>


")
  
  walk2(links, 1:length(links), function(link, index){
    print(glue('{index}. {link}'))
  })
}
```